Characterizing Signal Loss, Error, and Bias in the 21cm Reionization \\Power Spectrum: A Revised Study of PAPER-64

### 2017-12-01 PAPER.tex
added two new plots to the method2 appendix

@@

>>>>

\begin{figure}[tp]
\centering
\includegraphics[width=\textwidth]{plots/method2_heatmap_I.png}
\caption{The distribution of output power spectrum values for a 
given injection level P$_{in}$.\label{fig:Pr_vs_Pin}}
\end{figure}

@@

\begin{figure}[tp]
\centering
\includegraphics[width=.5\textwidth]{plots/method2_prob_vs_pinj.png}
\caption{The probability that an injected signal of level P$_{inj}$
is observable at a 2$\sigma$ level above the value of P$_{data}$.
\label{fig:Prob_vs_Pin}}
\end{figure}
